---
title: "Annual Reports"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Sidebar {.sidebar}
=====================================

```{r}
# shiny inputs defined here
```

Charts {data-navmenu="Fin Aid Summary"}
=====================================

Column {data-width=650}
-----------------------------------------------------------------------

### Cost of Attendance-Graduate

```{r}
pdf_tbl <- readRDS("pdf2.rds")
pdf_tbl
```

Column {data-width=350}
-----------------------------------------------------------------------

### Cost of Attendance-Graduate Resident

```{r echo=FALSE, COA-Grad-Resident}
c_pie_grad_res <- readRDS("c_pie_grad_res.rds")
c_pie_grad_res
```

### Cost of Attendance-Graduate NonResident

```{r}
c_pie_grad_res <- readRDS("c_pie_grad_non.rds")
c_pie_grad_non
```

ChartsTables {data-navmenu="Fin Aid Summary"}
=====================================


Row
-----------------------------------------------------------------------

### Cost of Attendance-Graduate Resident

```{r echo=FALSE, COA-Grad-ResidentA}
c_pie_grad_res <- readRDS("c_pie_grad_res.rds")
c_pie_grad_res
```

### Cost of Attendance-Graduate NonResident

```{r}
c_pie_grad_res <- readRDS("c_pie_grad_non.rds")
c_pie_grad_non
```

Row
-----------------------------------------------------------------------

### Cost of Attendance-Graduate

```{r}
pdf_tbl <- readRDS("pdf2.rds")
pdf_tbl
```

Tables {data-navmenu="Fin Aid Summary"}
=====================================  

Row
-------------------------------------
    
### Chart 1
    
```{r}
coa.gr.tree <- readRDS("coa.gr.tree.rds")
treemap(coa.gr.tree,                                                                                #Your data frame object
        index=c("residency","desc"),                                                                #A list of your categorical variables
        vSize = "cost",                                                                             #This is your quantitative variable
        type="index",                                                                               #Type sets the organization and color scheme of your treemap
        palette = "Blues",                                                                          #Select your color palette from the RColorBrewer presets or make your own.
        title="Cost of Attendance",                                                                 #Customize your title
        fontsize.title = 14                                                                         #Change the font size of the title
        )
```
   
Row
-------------------------------------
    
### Chart 2
    
```{r}

```
    
### Chart 3

```{r}

```

Charts {data-navmenu="UG COA"}
=====================================     

Column {data-width=350}
-----------------------------------------------------------------------

### Cost of Attendance-Graduate Resident

```{r echo=FALSE, COA-Grad-Resident2}
c_pie_grad_res <- readRDS("c_pie_grad_res.rds")
c_pie_grad_res
```

### Cost of Attendance-Graduate Non Resident

```{r}
t_coa <- readRDS("t_coa.rds")
t_coa
```

Tables {data-navmenu="UG COA"}
=====================================    

Row
-------------------------------------
    
### Cost of Attendance-Undergraduate Resident

```{r echo=FALSE, COA-Undergrad-Resident}
c_pie_ug_res <- readRDS("c_pie_ug_res.rds")
c_pie_ug_res
```
    
### Cost of Attendance-Undergraduate Non Resident

```{r echo=FALSE, COA-Undergrad-NonResident}
c_pie_ug_non <- readRDS("c_pie_ug_non.rds")
c_pie_ug_non
```

Row
-------------------------------------
    
### Chart 1
    
```{r}

```

Page 1 {data-navmenu="Fin Aid Awd"}
=====================================    

Row
-------------------------------------
    
### Financial Aid Award-Undergraduate Resident

```{r echo=FALSE, Fin-Aid-Awd-Undergrad-Resident}
c_pie_ug_res <- readRDS("c_pie_ug_res.rds")
c_pie_ug_res
```
    
### Financial Aid Award Non Resident

```{r echo=FALSE, Fin-Aid-Awd-NonResident}
c_pie_ug_non <- readRDS("c_pie_ug_non.rds")
c_pie_ug_non
```

Column
-------------------------------------
    
### Financial Aid Award
    
```{r}

```





Page 2 {data-navmenu="Fin Aid Awd"}
=====================================    

Column 
-------------------------------------
    
### Chart 1
    
```{r}
pdf_tbl <- readRDS("pdf2.rds")
pdf_tbl
```
   
Column {.tabset}
-------------------------------------
   
### Chart 2

```{r echo=FALSE, Fin-Aid-Awd2-Undergrad-Resident}
c_pie_ug_res <- readRDS("c_pie_ug_res.rds")
c_pie_ug_res
```   
 
### Chart 3
    
```{r echo=FALSE, Fin-Aid-Awd2-NonResident}
c_pie_ug_non <- readRDS("c_pie_ug_non.rds")
c_pie_ug_non
```