---
title: "Enrollment Trends"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: spacelab    
---

```{r setup, include=TRUE}
library(data.table)
library(dplyr)
library(DT)
library(flexdashboard)
library(formattable)
library(plotly)
library(treemap)
load("mu.RData")
```

Charts {data-navmenu="Enrollment Summary"}
=====================================

Row {data-width=500}
-----------------------------------------------------------------------

### Total Enrollment By Year

```{r echo=FALSE, Total-Enrollment-by-Year}
viz_bar_enroll_by_yr <- readRDS("viz_bar_enroll_by_yr.rds")
viz_bar_enroll_by_yr
```

Column {data-width=350}
-----------------------------------------------------------------------

### Six Year Enrollment Trend

```{r echo=FALSE, include=TRUE, Total-Enrollment-Trends}
valueBox(percent(enroll.delta.tot[1,1]), icon = "fa-pencil", href="#details")
```


### Enrollment TYpe by Year

```{r}
pdf3<-datatable((enroll.delta.type.length), options = list(
  searching = FALSE,
  paging = FALSE,
  lengthMenu = c(5, 10, 15, 20)
))
pdf3 <- formatPercentage(pdf3,9, digits = 0)
pdf3 <- formatCurrency(pdf3, 3:8, currency = "", interval = 3, mark = ",", digits = 0, before = TRUE)
pdf3
```


### Current Year Enrollment Treemap

```{r}
x<-enroll.delta.type.length[-5,c(1:2,8:9)]
  x$label <- paste(x$Type, x$Length, sep = "\n")
  treemap(x,
    index=c("label"),
    vSize="2016",
    vColor="itd_delta",
    type="value")     
```

Tables {data-navmenu="Enrollment Summary"}
=====================================  

Column
-------------------------------------
    
### Table 1
    
```{r}
knitr::kable(enroll.delta.type.length)
```
   
Row
-------------------------------------
    
### Table 2
    
```{r}

```
    
### Table 3

```{r}

```

Length {data-navmenu="Institution Overview"}
=====================================


Row
-----------------------------------------------------------------------

### Program Length - 2 Year

```{r echo=FALSE, Length-Two-Yr}
viz.line.length.yoy2 <- readRDS("viz.line.length.yoy2.rds")
viz.line.length.yoy2
```

Row
-----------------------------------------------------------------------

### Program Length - 4 Year

```{r echo=FALSE, Length-Four-Yr}
viz.line.length.yoy4 <- readRDS("viz.line.length.yoy4.rds")
viz.line.length.yoy4
```

Type {data-navmenu="Institution Overview"}
=====================================  

Row
-------------------------------------
    
### Program Type - Independent
    
```{r echo=FALSE, Type-Independent}
viz.line.type.ind <- readRDS("viz.line.type.ind.rds")
viz.line.type.ind
```
   
Row
-------------------------------------
    
### Program Type - Public
    
```{r echo=FALSE, Type-Public}
viz.line.type.public <- readRDS("viz.line.type.public.rds")
viz.line.type.public
```

Charts {data-navmenu="College Detail"}
=====================================     

Column {data-width=350}
-----------------------------------------------------------------------

### Cost of Attendance-Graduate Resident

```{r echo=FALSE, COA-Grad-Resident2}

```

### Cost of Attendance-Graduate Non Resident

```{r}

```

Tables {data-navmenu="College Detail"}
=====================================    

Row {data-width=450}
-------------------------------------
    
### Top 10 Institutions

```{r echo=FALSE, Top-10-Institutions}
delta.college<-data.table(enroll.delta.college[, c(3:5,2)])
delta.college[is.na(delta.college) ] <- 0

delta.college.top <- delta.college %>%
arrange(desc(itd_delta)) %>% 
slice(1:10) 

delta.college.top <- datatable((delta.college.top), options = list(
  searching = FALSE,
  paging = FALSE,
  lengthMenu = c(5, 10, 15, 20)
))
delta.college.top <- formatPercentage(delta.college.top, 4, digits = 2)
delta.college.top

```
    
### Bottom 10 Institutions

```{r echo=FALSE, Bottom-10-Institutions}
delta.college.bottom <- delta.college %>%
arrange(itd_delta) %>% 
slice(1:10) 

delta.college.bottom <- datatable((delta.college.bottom), options = list(
  searching = FALSE,
  paging = FALSE,
  lengthMenu = c(5, 10, 15, 20)
))
delta.college.bottom <- formatPercentage(delta.college.bottom, 4, digits = 2)
delta.college.bottom
```

Row
-------------------------------------
    
### Institutional Ranking
    
```{r}
viz.bar.college.rank <- readRDS("viz.bar.college.rank")
viz.bar.college.rank
```

Page 1 {data-navmenu="Fin Aid Awd"}
=====================================    

Row
-------------------------------------
    
### Financial Aid Award-Undergraduate Resident

```{r echo=FALSE, Fin-Aid-Awd-Undergrad-Resident}

```
    
### Financial Aid Award Non Resident

```{r echo=FALSE, Fin-Aid-Awd-NonResident}

```

Column
-------------------------------------
    
### Financial Aid Award
    
```{r}

```





Page 2 {data-navmenu="Fin Aid Awd"}
=====================================    

Column 
-------------------------------------
    
### Chart 1
    
```{r}

```
   
Column {.tabset}
-------------------------------------
   
### Chart 2

```{r echo=FALSE, Fin-Aid-Awd2-Undergrad-Resident}

```   
 
### Chart 3
    
```{r echo=FALSE, Fin-Aid-Awd2-NonResident}

```